### 2015-03-26 tex/proofs.tex
Added proofs and definitions to ./tex/paper.tex to create an extended version of the paper. Numerous corrections to proofs.tex

\begin{theorem}
If $R \subseteq F\sim(R)$, then $R$ is a bisimulation.
\label{lem:bisim}
\end{theorem}
The proof can be found in any good text on bisimulation.
%For the proof, we refer the reader to \cite{Sangiorgi:2011}

@@

\begin{lemma}[$\sqsubset$ is a bisimulation for $\rinit$ and $\rsum$]
\label{lem:init}
If $P \sqsubset q$ and if $\exists q^\prime (q \rsym q^\prime )$ , then $\exists 
\end{lemma}

\begin{proof}
In order for a state to be equivalent to a set of GSE states, it must be both sound and complete with respect to the set. We will begin the proof by showing completeness, and then finish by demonstrating soundness.

To show completeness, we must show that any state in the set is represented by $s_\sym$. The definition of representation requires the both the existence of a homomorphism, and proof that the homomorphism constraint is satisfiable. To show that a homomorphism exits, take any GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$. By Definition~\ref{representation}, we know $s_\gse = \lp \cfgnt{L}_\gse\ \cfgnt{R}_\gse\ \phi_\gse\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$. Take any state $s_\gse^\prime$ where $s_\gse \rinit^* s_\gse^\prime$, and state $s_\sym^\prime$ where $s_\sym \rsum^* s_\sym^\prime$. Note that  state $s_\gse^\prime$ has the form: $s_\gse^\prime = \lp \cfgnt{L}_{\gse^\prime}\ \cfgnt{R}_{\gse^\prime}\ \phi_{\gse^\prime}\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$.Take any location, field pair $\lp l_\gse\  \cfgnt{f}\rp$ such that $\lp l_\gse\  \cfgnt{f}\rp \in \cfgnt{R}_{\gse}^\leftarrow$, and let $l_\sym = h(l_\gse)$. We may classify $l_\gse$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $s_\gse$, $s_\gse^\prime$, $s_\sym$, and $s_\sym^\prime$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.

Class 1: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f} ) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f} ) = \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$.  Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\gse}(\cfgnt{R}_{\gse} (\cfgnt{l}_\gse,f )) $. In this case, let $h^\prime(l_\alpha) = h(l_\alpha)$. Since $s_\gse \rightharpoonup_h s_\sym$, we may surmise that: 
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$

Class 2: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$. Since $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$, the Summarize rule must have altered this reference. A reference created by the Summarize rule has a value set $\theta_{all}$ with four subsets: $\theta_{null}$, $\theta_{new}$, $\theta_{alias}$, and $\theta_\mathit{orig}$. Because $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) = \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_\mathit{orig}$. Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{\gse}(\cfgnt{R}_{\gse} (\cfgnt{l}_\gse,f )) $, and let $l_{orig} = h(l_\alpha)$. In this case, we let $h^\prime(l_\alpha) = h(l_\alpha)$. Since $(\phi_a\ l_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f ))$. Let $l_{orig} = h(l_\alpha)$. We can see that by the Summarize rule $ (\phi_b\ l_\mathit{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$, so therefore:
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$

Class 3: $\cfgnt{R}_\gse ( l_\gse,  \cfgnt{f}) \neq \cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_\sym,  \cfgnt{f}) \neq \cfgnt{R}_{s^\prime} ( l_\sym,  \cfgnt{f})$. In this case, there are two possibilities: either the new reference $\cfgnt{R}_{\gse^\prime} ( l_\gse,  \cfgnt{f})$ points to some location we've seen before $l_\alpha$, or it points to a previously unobserved location $l_\beta$. By establishing which of these possibilities has happened, we can build $h^\prime$. To construct $h^\prime$, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) $. If there exists $\phi_\alpha$ such that $\lp \phi_\alpha\ l_\alpha \rp \in \cfgnt{L}_{\gse}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$. Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_\sym,f )) $. Now, let $h^\prime(l_\alpha) = l_\beta$. Observe that either way,
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\gse,f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\sym,f ))$$

Furthemore, since $l_\alpha$ and $l_\beta$ are new locations with uninitialized fields, we know that for any field $f^\prime$, $\{(\phi_p\ \bot)\} = \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\alpha,f^\prime ))$ and $ \{(\phi_p\ \bot)\} = \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_\beta,f^\prime ))$ therefore, we know that:
$$(\phi_p\ \cfgnt{l}_x) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_\alpha,f^\prime )) \Rightarrow (\phi_q\ h^\prime (\cfgnt{l}_x))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} ( h^\prime(\cfgnt{l}_\alpha),f ))$$

We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{\gse^\prime}^\rightarrow$ such that:
$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{\gse^\prime}(\cfgnt{R}_{\gse^\prime} (\cfgnt{l}_{\gse^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\gse^\prime},f )) $$
By Definition~\ref{def:homomorphism} we know that $s_\gse^\prime \rightharpoonup_{h^\prime} s_\sym^\prime$.

It remains to show that $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime) )$. For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(s_\gse^\prime \rightharpoonup_{h} s_\sym^\prime)$, and therefore the satisfiability cannot be changed. For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_\mathit{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$. Constraints of the form  $\phi_x \wedge \phi_\mathit{orig}$ contain terms $\phi_x$ and $\phi_\mathit{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected. In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected. Since the previous heap constraint is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.

Since the heap constraint is satisfiable, we know that $s_\gse^\prime \sqsubset s_\sym^\prime $. We have therefore shown that for some symbolic state $s_\sym$ and an arbitrary GSE state $s_\gse$ such that $s_\gse \sqsubset s_\sym$ :
\begin{equation} 
(s_\gse \rinit^* s_\gse^\prime \wedge s_\sym \rsum^* s_\sym^\prime) \Rightarrow s_\gse^\prime \sqsubset s_\sym^\prime 
\end{equation}

We now prove the reverse case, that $s_\sym^*$ represents no infeasible states. Suppose that $s_\sym^\prime$ represents some infeasible state. This means that we represent some GSE state that has some reference r which points somewhere that no place in the feasible set points to. Since we don't change the path condition, all the old references still point exactly to the same places they used to.

So, the problem must be with one of the new references. All of the new references point to either a new location, the null location, the uninitialized location, or some alias. In the Summarize rule, the values and constraints for the new, null, uninitialized, and alias locations are contained in the sets $\theta_{new}$, $\theta_{null}$, $\theta_\mathit{orig}$, and $\theta_{alias}$. Since the null, and uninitialized locations are already accounted for by the homomorphism $s_\gse \rightharpoonup_h s_\sym$, and since a new location was created symmetrically for both $s_\gse^\prime$ and $s_\sym^\prime$, the problem must be with some alias location that is part of $s_\sym$ but not $s_\gse$. This means that there must be a feasible path to a target location that does not exist for any GSE heap. So, pick an arbitrary GSE heap containing the location and field in question. If said target location does not exist, then there is no reference in the GSE heap pointing to that location. In the symbolic heap, the path constraint on the path leading to the undesired target contains an aliasing condition that states that the source reference only points to this target location on condition that the parent reference points there. However, since we already know that no other reference in the GSE heap points there, this condition must be infeasible. Therefore, it is not part of the represented state. We have a contradiction. Therefore, there is no alias that points somewhere it's not supposed to.

We have now proven that 
$$ s_\gse^* \sqsubset s_\sym^*  \Rightarrow  s_\gse^* \in \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$
This fact, combined with our previous result, proves that
$$s_\sym^*  \cong \{\forall s_\gse^\prime | \exists s_\gse (s_\gse \sqsubset s_\sym \wedge (s_\gse \rinit^* s_\gse^\prime) ) \}$$

@@

Arbitrary P' such that P transitions to P'. Reason over each possible P' (how every many choices might exist--Only one for FA). Pick arbitrary p' in one of the sucessor. Do the forward proof. Show connection in q'. Connect to P' since it holds for arbitrary.

@@

\begin{proof}
Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.

\lemref{lem:succ} ensures at least one successor of $P$ and $q$. Let $p^\prime \in P^\prime$ be any
state in any successor set and $p \rgse p^\prime$ that state's
predecessor. Let $q^\prime$ be similarly defined relative to $q$.  The states $p$ and $q$, by virtue of the
representation relation, are only differentiated by their heaps and
global constraints since the environment ($\eta$), expression ($r$),
and continuation ($\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
\cfgnt{k}\rp$) are the same in all states 
(\defref{representation}).

There are two relations defined for field access in both $\rsgse$ and
$\rsym$ for a null and non-null pointing reference (\figref{fig:lazy}
and \figref{fig:fHeap}). In each relation, the environment is
unchanged. For a null pointing reference, in both relations, the
expression is $\cfgt{error}$ and the continuation is $\cfgt{end}$. For
the non-null pointing reference, some care is needed. First each does
use the same continuation $\cfgnt{k}$ (it is the same for $p$ and $q$
by $\sqsubset$. As the environment and continuations are the same,
$r^\prime = \mathrm{stack}_\cfgnt{r}()$, returns the same next largest
number of current stake references from the partition. The first
condition for inclusion in $\sqsubset$, equality between environments,
expressions, and continuations, is met.

@@

\noindent{\textrm{F{\footnotesize IELD}}
\textrm{A{\footnotesize CCESS (NULL)}}}: $p \rightarrow^\ell_\mathit{FA(N)}
p^\prime$ because $l = l_\mathit{null}$ (\figref{fig:lazy}). As $p$
is represented in $q$, $\exists q^\prime\ (q
\rightarrow^\sym_\mathit{FA{N}} q^\prime$ since $l_{\mathit{null}}$
must be feasible on the reference (\figref{fig:fHeap}).

@@

The final heap in the successor state $p^\prime$ is
$(\cfgnt{L}^\prime_p [\cfgnt{r}^\prime \mapsto
  \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime_p)$, and for $q^\prime$
the final heap in the successor state is
$(\cfgnt{L}^\prime_q[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp
  \cfgnt{L}^\prime_q,\cfgnt{R}^\prime_q,\cfgnt{r},\cfgnt{f},\phi^\prime_g\rp
]\ \cfgnt{R}^\prime_q)$; each version adding in the
constraint-location pair or value set respectively on the same
reference $\cfgnt{r}^\prime$. As $r^\prime$ is a stack reference, and
identical in both $p^\prime$ and $q^\prime$, and no new locations are
added to either heap, the existing homomorphism after initialization
still holds: $p^\prime \rightharpoonup_h q^\prime$.

 To relate $p^\prime$ and $q^\prime$ on
$\sqsubset$, it is necessary to create a new homomorphism:
$(\cfgnt{L}^\prime_p\ \cfgnt{R}^\prime_p) \rightharpoonup_{h^\prime}
(\cfgnt{L}^\prime_q\ \cfgnt{R}^\prime_q)$. To that end, construct the
function $h^\prime$ such that $h^\prime = h$.

>>>>

\begin{theorem}
If $R \subseteq F_\sim(R)$, then $R$ is a bisimulation.
\label{lem:bisim}
\end{theorem}
The proof can be found in any good text on bisimulation.
%For the proof, we refer the reader to \cite{Sangiorgi:2011}

@@

\begin{lemma}[Existence of Equivalent Initialized States]
\label{lem:init}
If we have state $q$, and set of states $P$ such that $q \in 2^{S_\mathit{FA}}$ and $P \sqsubset q$, then there exists state $q^+$ and set of states $P^+$ such that $P \sim P^+$, $q \sim q^+$, $P^+ \sqsubset q^+$, and all the relevant fields are initialized.
\end{lemma}

\begin{proof}
Our proof strategy is to take arbitrary $q$ and $P$, and then construct $q^+$ and $P^+$ such that $P \sim P^+$, $q \sim q^+$, and all the relevant fields are initialized. We then prove that $P^+ \sqsubset q^+$.

Let $q$ be any state such that $q \in 2^{S_\mathit{FA}}$, and let $P$ be a set of states such that $P \sqsubset q$. By Definition~\ref{representation}, $q = \lp \cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$. Let $q^+$ be the state such that $q^+ = \lp \cfgnt{L}_{q}^\prime\ \cfgnt{R}_{q}^\prime\ \phi_{q}\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ where $\cfgnt{L}_{q}^\prime$ and  $\cfgnt{R}_{q}^\prime$ are as defined in the $\rsym$ field access rule. Although the $\rsum$ relation does not relate states, we use the notation ${q} \rsum^* q^+$ to show this type of relationship between pairs of states. Let $p$ be any state such that $p \in P$. Define state $p^+$ in a similar fashion as $q^+$, except using the $\rgse$ field access rule. Define $P^+$ to be the set of all possible states like $p^+$: $P^+ = \{\forall {p}^+ | \exists {p} ({p} \sqsubset {q} \wedge ({p} \rinit^* {p}^+) ) \}$, and define $P^{q}$ to be the set of all states represented by $q^+$: $P^{q} = \{\forall {p}^\prime | {p}^\prime \sqsubset {q}^\prime \}$. Since $P^+$ and $q^+$ are simply pre-initialized versions of $P$ and $q$, it follows immediately that $P \sim P^+$ and $q \sim q^+$, and that all the relevant fields are initialized.

It remains to show that $P^+ \sqsubset q^+$. We will do so by proving that both $P^+ \subset P^q$ and $P^q \subset P^+$. From $p$, take any location, field pair $\lp l_p\  \cfgnt{f}\rp$ such that $\lp l_p\  \cfgnt{f}\rp \in \cfgnt{R}_{p}^\leftarrow$, and let $l_q = h(l_p)$. We may classify $l_p$ into one of three ways, based on the values of the $\cfgnt{R}$ function in each of the states $p$, $p^+$, $q$, and $q^+$, and we may define a function $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ based on that classification.

Class 1: $\cfgnt{R}_{p} ( l_{p},  \cfgnt{f} ) = \cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f} )$ and $\cfgnt{R}_{s} ( l_{q},  \cfgnt{f} ) = \cfgnt{R}_{q}^\prime ( l_{q},  \cfgnt{f})$.  Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{p}(\cfgnt{R}_{p} (\cfgnt{l}_{p},f )) $. In this case, let $h^\prime(l_\alpha) = h(l_\alpha)$. Since $p \rightharpoonup_h {q}$, we may surmise that: 
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f ))$$

Class 2: $\cfgnt{R}_{p} ( l_{p},  \cfgnt{f}) = \cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_{q},  \cfgnt{f}) \neq \cfgnt{R}_{q}^\prime ( l_{q},  \cfgnt{f})$. Since $\cfgnt{R}_{s} ( l_{q},  \cfgnt{f}) \neq \cfgnt{R}_{q}^\prime ( l_{q},  \cfgnt{f})$, the Summarize rule must have altered this reference. A reference created by the Summarize rule has a value set $\theta_{all}$ with four subsets: $\theta_{null}$, $\theta_{new}$, $\theta_{alias}$, and $\theta_\mathit{orig}$. Because $\cfgnt{R}_{p} ( l_{p},  \cfgnt{f}) = \cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f})$, we know that the location we want to map to lies in $\theta_\mathit{orig}$. Let $l_\alpha$ be the location such that ${(\phi_a\ l_\alpha)} = \cfgnt{L}_{p}(\cfgnt{R}_{p} (\cfgnt{l}_{p},f )) $, and let $l_{orig} = h(l_\alpha)$. In this case, we let $h^\prime(l_\alpha) = h(l_\alpha)$. Since $(\phi_a\ l_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f ))$. Let $l_{orig} = h(l_\alpha)$. We can see that by the Summarize rule $ (\phi_b\ l_\mathit{orig})\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f ))$, so therefore:
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f ))$$

Class 3: $\cfgnt{R}_{p} ( l_{p},  \cfgnt{f}) \neq \cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f})$ and $\cfgnt{R}_{s} ( l_{q},  \cfgnt{f}) \neq \cfgnt{R}_{q}^\prime ( l_{q},  \cfgnt{f})$. In this case, there are two possibilities: either the new reference $\cfgnt{R}_{p}^\prime ( l_{p},  \cfgnt{f})$ points to some location we've seen before $l_\alpha$, or it points to a previously unobserved location $l_\beta$. By establishing which of these possibilities has happened, we can build $h^\prime$. To construct $h^\prime$, let $l_\alpha$ be any location such that $(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f )) $. If there exists $\phi_\alpha$ such that $\lp \phi_\alpha\ l_\alpha \rp \in \cfgnt{L}_{p}^\rightarrow $, let $h^\prime(l_\alpha) = h(l_\alpha)$. Otherwise, let $l_\beta$ be the location such that $(\phi_b\ \cfgnt{l}_\beta) \in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f )) $ and $(\phi_b\ \cfgnt{l}_\beta) \notin \cfgnt{L}_{s}(\cfgnt{R}_{s} (\cfgnt{l}_{q},f )) $. Now, let $h^\prime(l_\alpha) = l_\beta$. Observe that either way,
$$(\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{p},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_{q},f ))$$

Furthemore, since $l_\alpha$ and $l_\beta$ are new locations with uninitialized fields, we know that for any field $f^\prime$, $\{(\phi_p\ \bot)\} = \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_\alpha,f^\prime ))$ and $ \{(\phi_p\ \bot)\} = \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime (\cfgnt{l}_\beta,f^\prime ))$ therefore, we know that:
$$(\phi_p\ \cfgnt{l}_x) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_\alpha,f^\prime )) \Rightarrow (\phi_q\ h^\prime (\cfgnt{l}_x))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{q}^\prime ( h^\prime(\cfgnt{l}_\alpha),f ))$$

We have now shown that there exists a mapping $h^\prime: \mathcal{L} \mapsto \mathcal{L}$ for all $\cfgnt{l}_{\gse^\prime} \in \cfgnt{L}_{p}^\prime^\rightarrow$ such that:
$$ (\phi_a\ \cfgnt{l}_\alpha) \in \cfgnt{L}_{p}^\prime(\cfgnt{R}_{p}^\prime (\cfgnt{l}_{\gse^\prime},f )) \Rightarrow (\phi_b\ h^\prime (\cfgnt{l}_\alpha))\in \cfgnt{L}_{s^\prime}(\cfgnt{R}_{s^\prime} (\cfgnt{l}_{\gse^\prime},f )) $$
By Definition~\ref{def:homomorphism} we know that $p^+ \rightharpoonup_{h^\prime} q^+$.

It remains to show that $\mathbb{S}( \phi_\sym^\prime \wedge \mathbb{HC}(p^+ \rightharpoonup_{h} q^+) )$. For locations in Class 1, no new conjuncts are added to $\mathbb{HC}(p^+ \rightharpoonup_{h} q^+)$, and therefore the satisfiability cannot be changed. For locations in Class 2 or Class 3, the new constraints take either the form $\phi_x \wedge \phi_\mathit{orig}$, or $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$. Constraints of the form  $\phi_x \wedge \phi_\mathit{orig}$ contain terms $\phi_x$ and $\phi_\mathit{orig}$ which were already conjoined to prior heap constraint, so satisfiability is not affected. In constraints of the form $\phi_x \wedge (r_f\ op\ r_{a}) \wedge (r_f\ op\ r_{b}) \wedge ...$, the term $\phi_x$ is conjoined to the prior heap constraint, and all the other terms involve the new variable $r_f$, so satisfiability is not affected. Since the previous heap constraint is satisfiable, and none of the new terms can impact the satisfiability, we know that the new heap constraint must also be satisfiable.

Since the heap constraint is satisfiable, we know that $p^+ \sqsubset q^+ $. We have therefore shown that for some symbolic state ${q}$ and an arbitrary GSE state $p$ such that $p \sqsubset {q}$ :
\begin{equation} 
(p \rinit^* p^+ \wedge {q} \rsum^* q^+) \Rightarrow p^+ \sqsubset q^+ 
\end{equation}

It follows immediately that $P^+ \subset P^q$. We now prove the reverse case, that $P^q \subset P^+$. Suppose that $q^+$ represents some infeasible state. This means that $q$ represents some GSE state that has some reference r which points somewhere that no place in the feasible set points to. Since the path condition is identical between $q$ and $q^+$, all references common to the two states point exactly to the same places under the same initial conditions.

So, the problem must be with one of the references which is present in $q^+$, but not $q$. All of these references point to either a new location, the null location, the uninitialized location, or some alias. In the Summarize rule, the values and constraints for the new, null, uninitialized, and alias locations are contained in the sets $\theta_{new}$, $\theta_{null}$, $\theta_\mathit{orig}$, and $\theta_{alias}$. Since the null, and uninitialized locations are already accounted for by the homomorphism $p \rightharpoonup_h {q}$, and since a new location was created symmetrically for both $p^+$ and $q^+$, the problem must be with some alias location that is part of ${q}$ but not $p$. This means that there must be a feasible path to a target location that does not exist for any GSE heap. So, pick an arbitrary GSE heap containing the location and field in question. If said target location does not exist, then there is no reference in the GSE heap pointing to that location. In the symbolic heap, the path constraint on the path leading to the undesired target contains an aliasing condition that states that the source reference only points to this target location on condition that the parent reference points there. However, since we already know that no other reference in the GSE heap points there, this condition must be infeasible. Therefore, it is not part of the represented state. We have a contradiction. Therefore, there is no alias that points somewhere it's not supposed to.

We have now proven that 
$$ {p}^* \sqsubset {q}^*  \Rightarrow  {p}^* \in \{\forall {p}^\prime | \exists {p} ({p} \sqsubset {q} \wedge ({p} \rinit^* {p}^\prime) ) \}$$
From this result, it is certain that $P^q \subset P^+$. This fact, combined with our previous result, proves that $P^q \cong P^+$. This, with our previous assumption that $P^{q} = \{\forall {p}^\prime | {p}^\prime \sqsubset {q}^\prime \}$, leads us to our final conclusion:
$$ P^+ \sqsubset q^+$$.

@@

Arbitrary P' such that P transitions to P'. Reason over each possible P' (how every many choices might exist--Only one for FA). Pick arbitrary p' in one of the successor. Do the forward proof. Show connection in q'. Connect to P' since it holds for arbitrary.

@@

\begin{proof}
%Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.

By \lemref{lem:init}, we may assume without loss of generality that \cfgnt{r} points to no locations where field \cfgnt{f} is uninitialized. Furthermore, \lemref{lem:succ} ensures at least one successor of $P$ and $q$. Let $p^\prime \in P^\prime$ be any
state in any successor set and $p \rgse p^\prime$ that state's
predecessor. Let $q^\prime$ be similarly defined relative to $q$.  The states $p$ and $q$, by virtue of the
representation relation, are only differentiated by their heaps and
global constraints since the environment ($\eta$), expression ($\cfgnt{r}$),
and continuation ($\lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow
\cfgnt{k}\rp$) are the same in all states 
(\defref{representation}).

There are two relations defined for field access in both $\rsgse$ and
$\rsym$ for a null and non-null pointing reference (\figref{fig:lazy}
and \figref{fig:fHeap}). In each relation, the environment is
unchanged. For a null pointing reference, in both relations, the
expression is $\cfgt{error}$ and the continuation is $\cfgt{end}$. For
the non-null pointing reference, some care is needed. First each does
use the same continuation $\cfgnt{k}$ (it is the same for $p$ and $q$
by $\sqsubset$. As the environment and continuations are the same,
$\cfgnt{r}^\prime = \mathrm{stack}_\cfgnt{r}()$, returns the same next largest
number of current stake references from the partition. The first
condition for inclusion in $\sqsubset$, equality between environments,
expressions, and continuations, is met.

@@

\noindent{\textrm{F{\footnotesize IELD}}
\textrm{A{\footnotesize CCESS (NULL)}}}: $p \rightarrow^\ell_\mathit{FA(N)}
p^\prime$ because $l = l_\mathit{null}$ (\figref{fig:lazy}). As $p$
is represented in $q$, $\exists q^\prime\ (q
\rightarrow^\sym_\mathit{FA(N)} q^\prime$ since $l_{\mathit{null}}$
must be feasible on the reference (\figref{fig:fHeap}).

@@

The final heap in the successor state $p^\prime$ is
$(\cfgnt{L}^\prime_p [\cfgnt{r}^\prime \mapsto
  \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime_p)$, and for $q^\prime$
the final heap in the successor state is
$(\cfgnt{L}^\prime_q[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp
  \cfgnt{L}^\prime_q,\cfgnt{R}^\prime_q,\cfgnt{r},\cfgnt{f},\phi^\prime_g\rp
]\ \cfgnt{R}^\prime_q)$; each version adding in the
constraint-location pair or value set respectively on the same
reference $\cfgnt{r}^\prime$. As $\cfgnt{r}^\prime$ is a stack reference, and
identical in both $p^\prime$ and $q^\prime$, and no new locations are
added to either heap, the existing homomorphism after initialization
still holds: $p^\prime \rightharpoonup_h q^\prime$.

 To relate $p^\prime$ and $q^\prime$ on
$\sqsubset$, it is necessary to create a new homomorphism:
$\gsest^\prime \rightharpoonup_{h^\prime}
\symst^\prime$. To that end, construct the
function $h^\prime$ such that $h^\prime = h$.
